Stat 400 Project

### 2021-11-22 Stat 400 proj.Rmd
Adding authors
Adding blank function to simluate SIR data, as well as providing df for their reported mc summary data.

---
title: "Stat 400 Project"
output: pdf_document
---

@@

```

>>>>

---
title: "Stat 400 Project"
authors: "Nathan Hemenway, Mark Hinds, Ian Hall"
output: pdf_document
---

@@

#S,I,R data
suceptable = function(){

recovered = function(){

infected = function(){

#reported monte carlo summary data
qd = c(0,25,50,75)
pos = c(99.3,99.2,98.7,92.7)
dncpv = c(69,53,46,33)
dncpt = c(26,32,43,42)
r0 = c(1.8,1.73,1.8,1.63)
mcsum = cbind(qd,pos,dncpv,dncpt,r0)
colnames(mcsum,c("Quarantine degree [%]",	"Percentage of size %",	"DNC peak value [cases]",	"DNC peaking time [days]",	"R0"))
```
